Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-07 WSSSPE3/report/wg_appendix_software_credit.tex
minor changes and fixes
Former-commit-id: bd71f53fc5aed4fe0bbfe0eb6f5d0d1e5b6ec452

There currently is no standard/accepted mechanism for citing software or receiving credit for software (akin to publications/citations).
Software is eligible for DOI assignment, but DOI metadata fields are not well tuned for software (vs. publications).
Some software providers apply for DOIs but it is still not a widely adopted.
Also, no mechanism to cite software dependencies within software.

Obstacle: indexers (e.g., Scopus) don’t currently support software/data document types or DataCite DOIs.

@@

The WSSSPE breakout group plans to join efforts related to citing softare with the FORCE11 Software Citation Working Group (FORCE11-SCWG)\footnote{FORCE11 Software Citation Working Group, \url{https://www.force11.org/group/software-citation-working-group}}; Kyle Niemeyer formally requested the merging of these groups following the meeting.
However, some future plans of the WSSSPE group fall outside the scope of FORCE11-SCWG, which covers software citation practices.
These activites include working with indexers such as Web of Science and Scopus to index software citations archived on, e.g., Zenodo\footnote{Zenodo, \url{https://zenodo.org}}, and pursuing the development of an open indexing service; such plans will be pursued either separately or through the formation of follow-on FORCE11 working groups.

@@

Following the meeting, Kyle Niemeyer formally requested the merging of software citation activities with FORCE11-SCWG.
Within a month of the meeting, Kyle will organize a virtual meeting of the group and lead the division of responsibilities for compiling existing practices of software citation and including software\slash products in promotion and tenure dossiers.
Building off of these efforts, the next major milestone is drafting the Software Citation Principles document in collaboration with the SCWG, targeted for April 2016.
While the existing directors of the SCWG, Arfon Smith and Dan Katz, lead the efforts of that group torwards the Software Citation Principles document, Kyle will help coordinate contributions from the WSSSPE group members.

>>>>

There currently is no standard/accepted mechanism for citing software or receiving credit for software (akin to publications/citations).
Software is eligible for DOI assignment, but DOI metadata fields are not well tuned or standardized for software (vs. publications).
Some software providers apply for DOIs but it is still not widely adopted.
Also, there is no mechanism to cite software dependencies within software.

Obstacle: indexers (e.g., Scopus, Web of Science, Google Scholar) don't currently support software/data document types or DataCite DOIs.

@@

The WSSSPE breakout group plans to join efforts related to citing software with the FORCE11 Software Citation Working Group (FORCE11-SCWG)\footnote{FORCE11 Software Citation Working Group, \url{https://www.force11.org/group/software-citation-working-group}}; Kyle Niemeyer formally requested the merging of these groups following the meeting.
However, some future plans of the WSSSPE group fall outside the scope of FORCE11-SCWG, which covers software citation practices.
These activities include working with indexers such as Web of Science and Scopus to index software citations archived on, e.g., Zenodo\footnote{Zenodo, \url{https://zenodo.org}}, and pursuing the development of an open indexing service; such plans will be pursued either separately or through the formation of follow-on FORCE11 working groups.

@@

Following the meeting, Kyle Niemeyer formally requested the merging of software citation activities with FORCE11-SCWG.
Within a month of the meeting, Kyle will organize a virtual meeting of the group and lead the division of responsibilities for compiling existing practices of software citation and including software\slash products in promotion and tenure dossiers.
Building off of these efforts, the next major milestone is drafting the Software Citation Principles document in collaboration with the SCWG, targeted for April 2016.
While the existing directors of the SCWG, Arfon Smith and Dan Katz, lead the efforts of that group towards the Software Citation Principles document, Kyle will help coordinate contributions from the WSSSPE group members.
